Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-03 doc/paper.tex
Update paper
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>

\section{Method}

@@

\section*{References}

>>>>

\section{Methods}

\subsection{Problem Formulation}

We train a PPO model in a Partially Observable Markov Decision Process (POMDP). A POMDP is defined by a tuple $(S, A, T, R, O, \Omega, \gamma)$. Here, $s \in S$ denotes the state the environment is in and $a \in A$ denotes an action the agent can take. Based on the state and the action taken, the agent receives an observation $o \in O$ which depends on the new environment state and the action taken by $O(o | s, a)$. $T(s' | s, a)$ denotes the state transfer function, which gives a new state based on the previous state and action. The environment we use is part of Minigrid \cite{minigrid}.

@@
